Paper with Response to Referee\\Multiple Sections Separate Page Numberings and Bibliography

### 2019-11-18 template/fantemplate_paper_rr_response/draft.tex
response to referee template

\input{fragments/preamble_packages.tex}
\input{fragments/preamble_layout.tex}
\input{fragments/preamble_citation.tex}
\bibliography{bib/ref_one, bib/ref_two}

@@

\title{Overleaf Package Template File}

@@

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

@@

>>>>

\input{fragments/preamble_packages.tex}
\input{fragments/preamble_layout.tex}
\input{fragments/preamble_citation.tex}

% Responses to Referees
\usepackage{blindtext}
\newcommand{\aptxspc}{1.8}
\newcommand{\rrquote}{1.1}
\newcommand{\rrxspc}{1.5}

\bibliography{bib/ref_one, bib/ref_two}

@@

\title{Paper with Response to Referee\\Multiple Sections Separate Page Numberings and Bibliography}

@@

According to ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

@@

\appendix

\pagenumbering{arabic}
\setcounter{page}{1}

\section{Data Details\label{app:data}}
\blindtext
\section{Derivations}
\blindtext
\section{Robustness Checks}
\Blindtext
\pagebreak
\clearpage

\setcounter{section}{0}
\renewcommand{\thesection}{\arabic{section}}
\pagenumbering{arabic}
\setcounter{page}{1}

\begin{refsection}
\section{Responses to Editors and Referees}
\begin{spacing}{\rrxspc}
We appreciate the insightful questions and helpful suggestions raised by the Associate editor, referee one, and referee two and three. An important paper discussed related issued \autocite{becker_human_1986, case_lasting_2005}. \blindtext
\end{spacing}

\section{Responses to Editor}
\begin{spacing}{\rrquote}
\end{spacing}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}

In Sections \ref{sec:data} and \ref{app:data}. \blindtext

\subsection{Editor Question One}
\begin{spacing}{\rrquote}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}
\end{spacing}

\begin{spacing}{\rrxspc}
\blindtext
\end{spacing}
\clearpage
\pagebreak

\section{Responses to Referee One}
\begin{spacing}{\rrquote}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}
\end{spacing}

\begin{spacing}{\rrxspc}
\blindtext
\end{spacing}

\subsection{Referee One Question One}
\begin{spacing}{\rrquote}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}
\end{spacing}

\begin{spacing}{\rrxspc}
\Blindtext
\end{spacing}

\subsection{Referee One Question Two}
\begin{spacing}{\rrquote}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}
\end{spacing}

\begin{spacing}{\rrxspc}
\Blindtext
\end{spacing}

\pagebreak
\begingroup
\setstretch{1.0}
%\setstretch{1.1}
\setlength\bibitemsep{0pt}
\printbibliography[heading=subbibliography]
\endgroup
\pagebreak
\end{refsection}
